---
title: "Assignment 1: R Markdown practice"
author: "Jackie Baek"
date: "2022-03-08"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    smart: true
    dev: svg
urlcolor: blue
---
# Section
**Section 102**

# Course Goals
By the end of the course, students will be able to: 

* Use [GitHub](www.rstudio.com) for creating a reproducible research document.

  -- My GitHub username is: *jackie0baek0.*

* Obtain, clean, transform, and visualize a dataset using the R programming language.

* Interpret and predict dataset trends using statistical inference and models.

* Critically examine and interpret statistical claims reported in mass media.

# Including Code
## Running R code in a code chunk

```{r}
x <- 2+2
x + 3
```
The output of the first line of code is not printed out because it is assigned to a variable instead.

The second line of output is printed out instrad, but this means that the calculated value has not been saved for future use.

## Displaying Graphs

```{r}
ggplot2::qplot(data = iris, x = Sepal.Length, y = Sepal.Width)
```







